But I can't preregister my research: Improving the reproducibility and transparency of ecology and conservation with adaptive preregistration for model-based research

### 2025-03-04 _analysis/ms.qmd
rm email addresses for non-corresponding authors

    email: chris.jones@delwp.vic.gov.au

@@

    email: jian.yen@delwp.vic.gov.au

@@

    orcid: 0000-0003-2443-4463

@@

    email: henry.wootton@delwp.vic.gov.au

@@

    email: lyndsey.vivian@delwp.vic.gov.au

@@

    email: goodm@unimelb.edu.au

@@

    email: david.duncan@unimelb.edu.au

@@

    email: lrumpff@unimelb.edu.au

@@

    email: fidlerfm@unimelb.edu.au

@@

keywords:
  - preregistration
  - transparency
  - reproducibility
  - modelling
  - ecology
  - conservation
  - open-science
  - research software engineering
affiliations:
  - id: aff1
    name: University of Melbourne
  - id: aff2
    name: Arthur Rylah Institute for Environmental Research
format:
  # preprint-typst:
    # fontsize: 11pt
    # mainfont: Libertinus Serif 
  # docx: default
  preprint-docx:
    toc: false
    number-sections: true
    highlight-style: github
  elsevier-pdf:
    journal:
      name: Journal Name
      formatting: preprint #review or doubleblind
      model: 3p
      layout: onecolumn
      cite-style: authoryear
      # graphical-abstract: "![](abstract.png)"
      # highlights:
        # - Highlight 1
        # - Highlight 2 
        # - Highlight 3
    keep-tex: true
bibliography: "references_obsidian.bib"
csl: methods-in-ecology-and-evolution.csl
---

@@

| Preregistration Version | Preregistration Process | Modelling and Analysis Process |
|------------------------|------------------------|------------------------|
| **Version 1:** (v0.10 – v0.8.1) | Establish problem context, study background and aims, describe data collection and data cleaning process, articulate modelling objectives, and specify candidate models. | Data cleaning and preparation undertaken concurrently by lead and supporting researchers due to limited resourcing and short timelines for project deliverables. Candidate models addressing different components of the research question were preregistered. Identify data structural properties and potential consequences for model fitting |
| **Version 2:** (v0.9.0-v.0.12.5) | Describe Pilot Analysis on data subset and specify registered flexibility in the form of decision heuristics. | Critical uncertainties in modelling decisions were articulated (e.g. how do we classify best flow regime based on inundation data?). In addition, data partitioning, exploratory data analysis, refined candidate models and model checking procedure preregistered |
| **Version 3:** (v0.13.0-v.0.20.1) | Describe Main Analysis, including specification of decision tree for model selection process based on results of pilot analysis. | Conducted modelling and analysis as outlined in preregistration. Reported deviations and rationale as necessary. |
|  |  |  |

>>>>

@@

@@

@@

@@

@@

@@

@@

@@

@@

keywords:
  - preregistration
  - transparency
  - reproducibility
  - modelling
  - ecology
  - conservation
  - open-science
  - research software engineering
  - id: aff1
    name: University of Melbourne
  - id: aff2
    name: Arthur Rylah Institute for Environmental Research
format:
  html:
   toc: true
   number-sections: true
   highlight-style: github
  # preprint-typst:
    # fontsize: 11pt
    # mainfont: Libertinus Serif 
  # docx: default
  preprint-docx:
    toc: false
    number-sections: true
    highlight-style: github
  elsevier-pdf:
    journal:
      name: Journal Name
      formatting: preprint #review or doubleblind
      model: 3p
      layout: onecolumn
      cite-style: authoryear
      # graphical-abstract: "![](abstract.png)"
      # highlights:
        # - Highlight 1
        # - Highlight 2 
        # - Highlight 3
    keep-tex: true
bibliography: "references_obsidian.bib"
csl: methods-in-ecology-and-evolution.csl

@@

| Preregistration Version | Preregistration Process | Modelling and Analysis Process |
|----|----|----|
| **Version 1:** (v0.10 – v0.8.1) | Establish problem context, study background and aims, describe data collection and data cleaning process, articulate modelling objectives, and specify candidate models. | Data cleaning and preparation undertaken concurrently by lead and supporting researchers due to limited resourcing and short timelines for project deliverables. Candidate models addressing different components of the research question were preregistered. Identify data structural properties and potential consequences for model fitting |
| **Version 2:** (v0.9.0-v.0.12.5) | Describe Pilot Analysis on data subset and specify registered flexibility in the form of decision heuristics. | Critical uncertainties in modelling decisions were articulated (e.g. how do we classify best flow regime based on inundation data?). In addition, data partitioning, exploratory data analysis, refined candidate models and model checking procedure preregistered |
| **Version 3:** (v0.13.0-v.0.20.1) | Describe Main Analysis, including specification of decision tree for model selection process based on results of pilot analysis. | Conducted modelling and analysis as outlined in preregistration. Reported deviations and rationale as necessary. |
|  |  |  |
